Using traffic analysis to identify The Second Generation Onion Router

### 2011-03-27 thesis/thesis.tex
Another paragraph to intro censorship

The goal of anonymity sometimes aligns with that of providing resistance to
censorship. Many censorship resistance systems are built on top of anonymity
providing designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a
censorship resistant system built on top of AN.ON
\parencite{springerlink:10.1007/3-540-44702-4_7}.  Anonymous publishing systems
such as Freedom \parencite{Goldberg:1999p2231} and Freenet
\parencite{Clarke:2001p2435} also provide some measure of censorship resistance.
The goal of aChord \parencite{Hazel:2002p6929} is to provide a distributed
lookup system for peer-to-peer publishing systems, based on Chord
\parencite{Stoica:2001:CSP:383059.383071}.

Censorship resistance in aChord and gnuNet
\parencite{Hazel:2002p6929}, Infranet \parencite{Feamster:2002p307}.

Anonymous networks by acting as a relay for network traffic, provide some level
of censorship resistance though these goals do not always align.

@@

Although Tor succeeds to a certain extent in providing anonymity and censorship
resistance. Under controlled conditions it is possible to distinguish Tor
traffic from other forms of encrypted traffic using traffic analysis. This makes
it easy for Tor users to be isolated and targeted for attack. Since Tor relies
on large numbers of users for the protections it provides, attacks that affect
the reliability of the network can discourage participation, making it
ineffective. This paper describes a simple traffic analysis technique which can
be used to distinguish Tor traffic from another form of commonly encrypted
traffic.

\section{Traffic Analysis}

Research into Tor weaknesses has included the use of hostile exit nodes to
capture private information \parencite{website:tor-password-leak}, attacks that
take advantages of web based technologies such as Javascript and Flash to reveal
user's identities \parencite{Abbott:2007p298} and a number of identity revealing
traffic analysis techniques
\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}.
\citeauthor{McLachlan:2009p197} reveals a method for identifying bridge
operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.  It
is believed that this is the first proposal of a traffic analysis technique for
classification of Tor network streams.

>>>>

Providing resistance to blocking or censorship comes in many forms. The People's
Republic of China operates a sophisticated Internet firewall capable of blocking
requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
This system is often referred to as the Great Firewall of China. Resisting this
system can involve ignoring spurious reset packets injected into the stream of
forbidden communications \parencite{springerlink:10.1007/11957454_2}, or be as
simple as accessing data through an encrypted proxy as is done in FreeGate
\parencite{Smart:2008kx}.

The goal of anonymity sometimes aligns with that of providing resistance to
censorship. Many censorship resistance systems are built on top of anonymity
providing designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a
censorship resistant system built on top of AN.ON
\parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
aim to provide censorship resistance as well as anonymity. Infranet uses
steganography to hide sensitive messages in innocuous content Infranet
\parencite{Feamster:2002p307}.

@@

%Although Tor succeeds to a certain extent in providing anonymity and censorship
%resistance. Under controlled conditions it is possible to distinguish Tor
%traffic from other forms of encrypted traffic using traffic analysis. This makes
%it easy for Tor users to be isolated and targeted for attack. Since Tor relies
%on large numbers of users for the protections it provides, attacks that affect
%the reliability of the network can discourage participation, making it
%ineffective. This paper describes a simple traffic analysis technique which can
%be used to distinguish Tor traffic from another form of commonly encrypted
%traffic.

\section{Tor Weaknesses}

Research into Tor weaknesses has included the use of hostile exit nodes to
capture private information \parencite{website:tor-password-leak}, attacks that
take advantages of web based technologies such as Javascript and Flash to reveal
user's identities \parencite{Abbott:2007p298} and a number of identity revealing
traffic analysis techniques
\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}.
\citeauthor{McLachlan:2009p197} reveals a method for identifying bridge
operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.
